The Dark \LaTeX{} \\ \large An Example of the dndbook Class

### 2021-01-26 example.tex

\title{
  \Huge \scshape \fontfamily{pbk}\selectfont
  The Dark \LaTeX{} \\
  \medskip
  \normalfont
  \large
  An Example of the dndbook Class
}
\author{The rpgTeX Team \and Steve}
\date{}

@@

The command |\DndMap{title}| creates a new map index (A, B, C\ldots). This doesn't add anything to the document, but the map index can be referenced with |\ref{map:title}|. For example, the Kingdom is map\,\ref{map:The Kingdom}.

\DndMap{The Kingdom}

Areas can be references with |\ref{area:name}|. For example, Mount Doofus is area \ref{area:Mount Doofus}.

@@

\section{Map References}

\DndArea[The Kingdom]{Mount Doofus}
This area has a map reference before the number. The map name is an optional parameter on |\DndArea|. Useful if your document contains multiple maps!

@@

\begin{DndSidebar}[float=!b]{Behold the DndSidebar!}
\tocside{Behold the DndSidebar!}
  The |DndSidebar| is used as a sidebar. It does not break over columns and is best used with a figure environment to float it to one corner of the page where the surrounding text can then flow around it.

  Use the |\tocside{title}| command to create an entry in the table of contents, if you want.
\end{DndSidebar}

@@

\begin{lstlisting}[basicstyle=\ttfamily\small]
\begin{DndTable}[color=PhbLightCyan]{cX}
  d8 & Item \\
  1  & Small wooden button \\
  2  & Red feather \\
  3  & Human tooth \\
  4  & Vial of green liquid \\
  5  & Loaded dice \\
  6  & Tasty biscuit \\
  7  & Broken axe handle \\
  8  & Tarnished silver locket \\
\end{DndTable}
\end{lstlisting}

\begin{DndTable}[color=PhbLightCyan]{cX}
  d8 & Item \\
  1  & Small wooden button \\
  2  & Red feather \\
  3  & Human tooth \\
  4  & Vial of green liquid \\
  5  & Loaded dice \\
  6  & Tasty biscuit \\
  7  & Broken axe handle \\
  8  & Tarnished silver locket \\
\end{DndTable}

@@

\part{Appendices}

\appendix

\chapter{One Last Thing}

\DndDropCapLine{U}sing the |\appendix| command causes all subsequent chapters to be formatted as appendices. Neat!

>>>>

\title{The Dark \LaTeX{} \\
\large An Example of the dndbook Class}
\author{The rpgTeX Team}
\date{2020/04/21}

@@

@@

@@

\begin{DndSidebar}[float=!b]{Behold the DndSidebar!}
  The |DndSidebar| is used as a sidebar. It does not break over columns and is best used with a figure environment to float it to one corner of the page where the surrounding text can then flow around it.
\end{DndSidebar}

@@

\begin{lstlisting}[basicstyle=\ttfamily\small]
\begin{DndTable}[color=PhbLightCyan]{cX}
  d8 & Item \\
  1  & Small wooden button \\
  2  & Red feather \\
  3  & Human tooth \\
  4  & Vial of green liquid \\
  6  & Tasty biscuit \\
  7  & Broken axe handle \\
  8  & Tarnished silver locket \\
\end{DndTable}
\end{lstlisting}

\begin{DndTable}[color=PhbLightCyan]{cX}
  d8 & Item \\
  1  & Small wooden button \\
  2  & Red feather \\
  3  & Human tooth \\
  4  & Vial of green liquid \\
  6  & Tasty biscuit \\
  7  & Broken axe handle \\
  8  & Tarnished silver locket \\
\end{DndTable}

@@
